---
title: "Unit 03 Assignment"
author: "David Stroud"
date: "1/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Questions
##1. GitHub Cloning

>davidstroud (master) PublicData  
$ git clone https://github.com/awesomedata/awesome-public-datasets.git  
Cloning into 'awesome-public-datasets'...  
remote: Counting objects: 1427, done.  
remote: Total 1427 (delta 0), reused 0 (delta 0), pack-reused 1427  
Receiving objects: 100% (1427/1427), 497.07 KiB | 2.28 MiB/s, done.  
Resolving deltas: 100% (830/830), done.  
davidstroud (master) PublicData  
$ ls  
awesome-public-datasets  
davidstroud (master) PublicData  
$ cd awesome-public-datasets/  
davidstroud (master) awesome-public-datasets  
>

##2. Data Summary

```{r}
# a. Read in titantic data set and assign to df
library(readr)
df <- read_csv("PublicData/awesome-public-datasets/Datasets/titanic.csv")
```

```{r}
# b. Output the respective count of females and males aboard the Titanic. Plot the frequency of females and males.  Be sure to give an accurate title and label the axes.


```

```{r}
# c.Please use one apply function to output the means of Age, Fare, and Survival.  
MyList <- list(df$Age,df$Fare,df$Survived)
sapply(MyList, mean, na.rm=TRUE)

```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
