---
title: "Unit 03 Assignment"
author: "David Stroud"
date: "1/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Questions
##1. GitHub Cloning  
* #### Using Git, clone the following GitHub repository to your local machine: https://github.com/caesar0301/awesome-public-datasets.  

>davidstroud (master) PublicData  
$ git clone https://github.com/awesomedata/awesome-public-datasets.git  
Cloning into 'awesome-public-datasets'...  
remote: Counting objects: 1427, done.  
remote: Total 1427 (delta 0), reused 0 (delta 0), pack-reused 1427  
Receiving objects: 100% (1427/1427), 497.07 KiB | 2.28 MiB/s, done.  
Resolving deltas: 100% (830/830), done.  
davidstroud (master) PublicData  
$ ls  
awesome-public-datasets  
davidstroud (master) PublicData  
$ cd awesome-public-datasets/  
davidstroud (master) awesome-public-datasets  
>

##2. Data Summary

```{r}
# a. Read in titantic data set and assign to df
library(readr)
df <- read_csv("PublicData/awesome-public-datasets/Datasets/titanic.csv")
```

```{r}
# b. Output the respective count of females and males aboard the Titanic. Plot the frequency of females and males.  Be sure to give an accurate title and label the axes.
df$Sex <- as.factor(df$Sex)
summary(df$Sex)
```

```{r}
# c.Please use one apply function to output the means of Age, Fare, and Survival.  
MyList <- list(df$Age,df$Fare,df$Survived)
sapply(MyList, mean, na.rm=TRUE)

```


## 3. Function Building

```{r}
library(readr)
# Import sleep data
sleep <- read_csv("sleep_data_01.csv")

# Create SleepData function
SleepData <- function(report) {
  # a. Create objects for the median Age, the minimum and maximum Duration of sleep,   and the mean and standard deviation of the Rosenberg Self Esteem scale (RSES).  
  AgeMed <- median(sleep$Age,na.rm = TRUE)
  DurMin <- min(sleep$Duration,na.rm = TRUE)
  DurMax <- max(sleep$Duration,na.rm = TRUE)
  RsesAvg <-mean(sleep$RSES,na.rm=TRUE)
  RsesSd <-sd(sleep$RSES,na.rm=TRUE)
  
  # b. Create a data.frame object called report: 
  report <- data.frame(AgeMed/5,RsesAvg/5,RsesSd/5,(DurMax-DurMin))
  
 # c.	Change the column names of this data.frame to MedianAge, SelfEsteem, SE_SD,     and DurationRange
  colnames(report)[1] <- "MedianAge"
  colnames(report)[2] <- "SelfEsteem"
  colnames(report)[3] <- "SE_SD"
  colnames(report)[4] <- "DurationRange"
  return(report)
}

# e. Run sleep data function to show output
SleepData()

```






